The Response Time of Toronto's Paramedic Service: How effective is the city's emergency medical care?

### 2023-02-04 outputs/paper/paper.qmd
Added legend to graphs

  # Define axis labels
  labs(y = "Emergency Responses", x = "Year") +

@@

  # Set axis formats
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  scale_x_continuous(breaks=seq(2014,2021,1)) +

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#| fig-cap: "Percent of Calls Meeting Mandated Response Times (since 2013)"
#| label: fig-4
#### Create graphs plotting mandated and actual response times ####
clean_response_data |>
  # Plot graphs, define x axis
  ggplot(aes(x=response_time_standard_year)) +

  # Define axis labels
  labs(y = "% of Calls Meeting Response Time", x = "Year") +

@@

  # Rotate X-axis labels
  theme(axis.text.x = element_text(angle=70, vjust=0.7)) +

  # Set axis formats
  scale_x_continuous(breaks=seq(2013,2021,2)) +

  # Render lines
  geom_line(aes(y = plan_in_percentage), color = "darkred") + 
  geom_line(aes(y = performance_in_percentage), color="steelblue") +

  guides(shape=TRUE) +

>>>>

  # Define axis labels
  labs(y = "Emergency Medical Responses", x = "Year") +

@@

  # Define styles
  theme(
    axis.title.x = element_text(size = 9, family = "serif", face = "bold"),
    axis.text.x = element_text(size = 8, family = "serif"),
    axis.title.y = element_text(size = 9, family = "serif", face = "bold"),
    axis.text.y = element_text(size = 8, family = "serif")
  ) +

  # Set axis formats
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  scale_x_continuous(breaks = seq(2014, 2021, 1)) +

@@

```{r}
#| messages: false
#| echo: false
#| warning: false
#| label: fig-4
#| fig-cap: "Percent of Calls Meeting Mandated Response Times (since 2013)"
#| fig-align: center
#| fig-width: 10
#| fig-height: 5
#### Create graphs plotting mandated and actual response times ####
colors <- c("Actual Response" = "steelblue", "Mandated Response" = "darkred")

clean_response_data |>
  # Plot graphs, define x axis
  ggplot(aes(x = response_time_standard_year)) +

  # Define axis labels
  labs(
    y = "Percent of Calls", 
    x = "Year",
    color = "Legend"
  ) +

@@

  # Rotate X-axis labels
  theme(
    axis.title.x = element_text(size = 15, family = "serif", face = "bold"),
    axis.text.x = element_text(size = 14, family = "serif", angle = 70, vjust = 0.7),
    axis.title.y = element_text(size = 15, family = "serif", face = "bold"),
    axis.text.y = element_text(size = 14, family = "serif"),
    legend.title = element_text(size = 15, family = "serif", face = "bold"),
    legend.text = element_text(size = 14, family = "serif"),
    strip.text.x = element_text(size = 15, family = "serif", face = "bold"),
    strip.text.y = element_text(size = 14, family = "serif", face = "bold")
  ) +

  # Set axis formats
  scale_x_continuous(breaks=seq(2013, 2021, 2)) +

  # Render lines
  geom_line(aes(y = plan_in_percentage, color = "Mandated Response")) + 
  geom_line(aes(y = performance_in_percentage, color = "Actual Response")) +

  scale_color_manual(values = colors) +
